CommonMind Consortium: DLPFC

### 2020-10-13 combined_analysis/CTS/GABA.Rmd
drop genes that don't vary

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)
```

>>>>

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)

# only keep genes common to both cohorts
isexpr = intersect(rownames(vobj.lst[[1]]), rownames(vobj.lst[[2]]))

vobj.lst = lapply(vobj.lst, function(vobj){
  vobj[isexpr,]
  })
```

### 2020-10-13 combined_analysis/CTS/MgAs.Rmd
drop genes that don't vary

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)
```

@@

  fit = dream(vobj[keep.ensID,], form_use, info, BPPARAM = SnowParam(18))  
  eBayes( fit )
  })
names(fit_inter_sex.disease.lst) = names(vobj.lst)

>>>>

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)

# only keep genes common to both cohorts
isexpr = intersect(rownames(vobj.lst[[1]]), rownames(vobj.lst[[2]]))

@@

  fit = dream(vobj[keep.ensID,], form_use, info, BPPARAM = SnowParam(4))  
  eBayes( fit )
  })
names(fit_inter_sex.disease.lst) = names(vobj.lst)

### 2020-10-13 combined_analysis/CTS/Olig.Rmd
drop genes that don't vary

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)
```

>>>>

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)

# only keep genes common to both cohorts
isexpr = intersect(rownames(vobj.lst[[1]]), rownames(vobj.lst[[2]]))

vobj.lst = lapply(vobj.lst, function(vobj){
  vobj[isexpr,]
  })
